Viral Sequence Sorting Tools Evaluation

### 2022-10-05 TestingPipeline/Scripts/comparing_rule_sets.Rmd
Added lake michigan and TARA identifying viral contigs directories

```{r setup-library}
library(ggplot2)
library(plyr)
library(reshape2)
library(viridis)
library(tidyr)
library(dplyr)
library(readr)
library(data.table)
```

@@

```{r inputs}
# dataset name for file organization and outputs for metrics file
dataset_name <- "testing_set"
# checkV
checkV_path <- "TestingSetToolOutputs/testing_sets_checkv_output.tsv"
# VIBRANT
vibrant_path <- "TestingSetToolOutputs/testing_sets_vibrant_output.tsv"
# DeepVirFinder
dvf_path <- "TestingSetToolOutputs/testing_sets_deepvirfinder_output.tsv"
# Virsorter
vs_path <- "TestingSetToolOutputs/testing_sets_virsorter_output.tsv"
# Virsorter2
vs2_path <- "TestingSetToolOutputs/testing_sets_virsorter2_output.tsv"
# Kaiju
kj_path <- "TestingSetToolOutputs/merged.nreuk.kaiju.names.out"
# KB cutoff
KB_CUTOFF <- 3000

```

@@

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7] <- keep_score[input_seqs$score>=0.7] + 0.5
#   keep_score[input_seqs$score>=0.9] <- keep_score[input_seqs$score>=0.9] + 0.5
  }

  if (include_kaiju) {
    keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] <- keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] - 1
    keep_score[input_seqs$Kaiju_Viral=="Viruses"] <- keep_score[input_seqs$Kaiju_Viral=="Viruses"] + 1
  }

@@

}

```

@@

  precision <- table(confusion_matrix)[4]/(table(confusion_matrix)[4]+table(confusion_matrix)[2])

  recall <- table(confusion_matrix)[4]/(table(confusion_matrix)[4]+table(confusion_matrix)[1])

  F1 <- 2*precision*recall/(precision+recall)

@@

this function builds a list of all of the combinations that the user wants to 
test. 
In this case, we're comparing the performance of all unique combinations of the 
six tools.
```{r}
build_score_list <- function(input_seqs, combos) {
  output <- data.frame(precision=rep(0, nrow(combos)),
                       recall=rep(0, nrow(combos)),
                       F1=rep(0, nrow(combos)))
  for (i in 1:nrow(combos)) {
    keep_score <- getting_viral_set_1(input_seqs, include_vibrant = combos$VIBRANT[i],
                                            include_virsorter = combos$VS[i],
                                            include_virsorter2 = combos$VS2[i],
                                            include_checkV = combos$CheckV[i],
                                            include_kaiju = combos$Kaiju[i],
                                            include_deepvirfinder = combos$DVF[i])

@@

## Calculate the performance of each pipeline
```{r}
accuracy_scores <- build_score_list(viruses[viruses$Index==1], combos_list)

accuracy_scores <- data.frame(testing_set_index=rep(0, nrow(combos_list)*10),
                      precision=rep(0, nrow(combos_list)*10),
                       recall=rep(0, nrow(combos_list)*10),
                       F1=rep(0, nrow(combos_list)*10))

accuracy_scores <- cbind(testing_set_index=rep(1, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==1], combos_list))

for (i in 2:10) {
  accuracy_scores <- rbind(accuracy_scores,
                           cbind(testing_set_index=rep(i, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==i], combos_list)))
}

```

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")

p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("F1 Score")

p2

ggplot(accuracy_scores, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Precision")

ggplot(accuracy_scores, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Recall")
```

>>>>

```{r setup-library}
library(ggplot2)
library(plyr)
library(reshape2)
library(viridis)
library(tidyr)
library(dplyr)
library(readr)
library(data.table)
options(warn=-1)
```

@@

```{r inputs}
# dataset name for file organization and outputs for metrics file
dataset_name <- "testing_set"
# checkV
checkV_path <- "../ToolOutput/testing_sets_checkv_output.tsv"
# VIBRANT
vibrant_path <- "../ToolOutput/testing_sets_vibrant_output.tsv"
# DeepVirFinder
dvf_path <- "../ToolOutput/testing_sets_deepvirfinder_output.tsv"
# Virsorter
vs_path <- "../ToolOutput/testing_sets_virsorter_output.tsv"
# Virsorter2
vs2_path <- "../ToolOutput/testing_sets_virsorter2_output.tsv"
# Kaiju
kj_path <- "../ToolOutput/merged.nreuk.kaiju.names.out"
# KB cutoff
KB_CUTOFF <- 3000
```

@@

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7] <- keep_score[input_seqs$score>=0.7] + 0.5
#   keep_score[input_seqs$score>=0.9] <- keep_score[input_seqs$score>=0.9] + 0.5
  }
  if (include_kaiju) {
    keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] <- keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] - 1
    keep_score[input_seqs$Kaiju_Viral=="Viruses"] <- keep_score[input_seqs$Kaiju_Viral=="Viruses"] + 1
  }

@@

}
```

this rule set is based on an original set of rules considered for analyzing the
drinking water virome. upon analyzing the sequences, many false positive viruses
were identified (particularly long sequences with no viral genes)
note: checkV is used as a viral sorting tool
note: VirFinder was used not DeepVirFinder
```{r getting_viral_set_2}
getting_viral_set_2 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_checkV=FALSE,
                                include_virsorter=FALSE) {

  if (include_vibrant) {
    keep_score[input_seqs$vibrant_quality=="high quality draft"] <- keep_score[input_seqs$vibrant_quality=="high quality draft"] + 1
    keep_score[input_seqs$vibrant_quality=="medium quality draft"] <- 
      keep_score[input_seqs$vibrant_quality=="medium quality draft"] + 0.5
    keep_score[input_seqs$vibrant_quality=="low quality draft"] <- keep_score[input_seqs$vibrant_quality=="low quality draft"] + 0.3
  }

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50] <- keep_score[input_seqs$viral>=50] + 0.3
    keep_score[(input_seqs$viral>=50 & input_seqs$host_genes==0) & input_seqs$viral_genes==0] <- 
      keep_score[(input_seqs$viral>=50 & input_seqs$host_genes==0) & input_seqs$viral_genes==0] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 1
    keep_score[input_seqs$hallmark>2] <- keep_score[input_seqs$hallmark>2] + 1
    }

  if (include_virsorter) {
    keep_score[input_seqs$category==1] <- keep_score[input_seqs$category==1] + 1
    keep_score[input_seqs$category==2] <- keep_score[input_seqs$category==2] + 0.5
    keep_score[input_seqs$category==3] <- keep_score[input_seqs$category==3] + 0.3
    keep_score[input_seqs$category==4] <- keep_score[input_seqs$category==4] + 1
    keep_score[input_seqs$category==5] <- keep_score[input_seqs$category==5] + 0.5
    keep_score[input_seqs$category==6] <- keep_score[input_seqs$category==6] + 0.3
  }

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7] <- keep_score[input_seqs$score>=0.7] + 0.5
    keep_score[input_seqs$score>=0.9] <- keep_score[input_seqs$score>=0.9] + 1
  }

  if (include_checkV) {
    keep_score[input_seqs$checkv_quality=="low"] <- keep_score[input_seqs$checkv_quality=="low"] + 0.3
    keep_score[input_seqs$checkv_quality=="medium"] <- keep_score[input_seqs$checkv_quality=="medium"] + 0.5
    keep_score[input_seqs$checkv_quality=="high"] <- keep_score[input_seqs$checkv_quality=="medium"] + 1

    keep_score[input_seqs$viral_genes==0 & input_seqs$host_genes>1] <- 0
  }

}
```

this is the set of rules used in the drinking water viromes paper
note: VirFinder was used not DeepVirFinder
```{r getting_viral_set_3}
getting_viral_set_3 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_checkV=FALSE,
                                include_virsorter=FALSE) {

  if (include_vibrant) {
    keep_score[input_seqs$vibrant_quality=="high quality draft"] <- keep_score[input_seqs$vibrant_quality=="high quality draft"] + 1
    keep_score[input_seqs$vibrant_quality=="medium quality draft"] <- 
      keep_score[input_seqs$vibrant_quality=="medium quality draft"] + 0.5
    keep_score[input_seqs$vibrant_quality=="low quality draft"] <- keep_score[input_seqs$vibrant_quality=="low quality draft"] + 0.3
  }

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50] <- keep_score[input_seqs$viral>=50] + 0.3
    keep_score[(input_seqs$viral>=50 & input_seqs$host_genes==0) & input_seqs$viral_genes==0] <- 
      keep_score[(input_seqs$viral>=50 & input_seqs$host_genes==0) & input_seqs$viral_genes==0] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 1
    keep_score[input_seqs$hallmark>2] <- keep_score[input_seqs$hallmark>2] + 1
    }

  if (include_virsorter) {
    keep_score[input_seqs$category==1] <- keep_score[input_seqs$category==1] + 1
    keep_score[input_seqs$category==2] <- keep_score[input_seqs$category==2] + 0.5
    keep_score[input_seqs$category==3] <- keep_score[input_seqs$category==3] + 0.3
    keep_score[input_seqs$category==4] <- keep_score[input_seqs$category==4] + 1
    keep_score[input_seqs$category==5] <- keep_score[input_seqs$category==5] + 0.5
    keep_score[input_seqs$category==6] <- keep_score[input_seqs$category==6] + 0.3
  }

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7] <- keep_score[input_seqs$score>=0.7] + 0.5
    keep_score[input_seqs$score>=0.9] <- keep_score[input_seqs$score>=0.9] + 1
  }

  if (include_checkV) {
    keep_score[input_seqs$viral_genes==0 & input_seqs$host_genes>=1] <- 0
    keep_score[(input_seqs$viral_genes*3) <= input_seqs$host_genes] <- 0
    keep_score[input_seqs$contig_length>50000 & input_seqs$hallmark==0] <- 0
  }

}
```

@@

  precision <- table(confusion_matrix)[4]/(table(confusion_matrix)[4]+table(confusion_matrix)[2])
  recall <- table(confusion_matrix)[4]/(table(confusion_matrix)[4]+table(confusion_matrix)[1])
  F1 <- 2*precision*recall/(precision+recall)

@@

this function builds a list of all of the combinations that the user wants to 
test. 
In this case, we're comparing the performance of all unique combinations of the 
six tools.
```{r}
build_score_list <- function(input_seqs, combos, pipeline) {
  output <- data.frame(precision=rep(0, nrow(combos)),
                       recall=rep(0, nrow(combos)),
                       F1=rep(0, nrow(combos)))
  for (i in 1:nrow(combos)) {
    if (pipeline==1) {
      keep_score <- getting_viral_set_1(input_seqs, include_vibrant = combos$VIBRANT[i],
                                              include_virsorter = combos$VS[i],
                                              include_virsorter2 = combos$VS2[i],
                                              include_checkV = combos$CheckV[i],
                                              include_kaiju = combos$Kaiju[i],
                                              include_deepvirfinder = combos$DVF[i])
    }
    if (pipeline==2) {
      keep_score <- getting_viral_set_2(input_seqs, include_vibrant = combos$VIBRANT[i],
                                              include_virsorter = combos$VS[i],
                                              include_virsorter2 = combos$VS2[i],
                                              include_checkV = combos$CheckV[i],
                                              include_deepvirfinder = combos$DVF[i])
    }
    if (pipeline==3) {
      keep_score <- getting_viral_set_3(input_seqs, include_vibrant = combos$VIBRANT[i],
                                              include_virsorter = combos$VS[i],
                                              include_virsorter2 = combos$VS2[i],
                                              include_checkV = combos$CheckV[i],
                                              include_deepvirfinder = combos$DVF[i])
    }

@@

## Calculate the performance of each pipeline
first rule set
```{r}
accuracy_scores <- data.frame(testing_set_index=rep(0, nrow(combos_list)*10),
                      precision=rep(0, nrow(combos_list)*10),
                       recall=rep(0, nrow(combos_list)*10),
                       F1=rep(0, nrow(combos_list)*10))
accuracy_scores <- cbind(testing_set_index=rep(1, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==1], combos_list, pipeline=1))
for (i in 2:10) {
  accuracy_scores <- rbind(accuracy_scores,
                           cbind(testing_set_index=rep(i, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==i], combos_list, pipeline=1)))
}
```

```{r}
library("stringr")
accuracy_scores$numtools <- str_count(accuracy_scores$toolcombo, "1")
accuracy_scores <- accuracy_scores[order(accuracy_scores$numtools, decreasing=F),]
accuracy_scores$toolcombo <- factor(accuracy_scores$toolcombo, levels = unique(accuracy_scores$toolcombo))
accuracy_scores$numtools <- as.factor(accuracy_scores$numtools)
```

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("F1 Score")
p2
ggplot(accuracy_scores, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Recall")
```
## Calculate the performance of each pipeline
original rule set from DW paper (didn't use)

```{r}
combos_list_3 <- read_csv("combinations_list_3.csv")
```

```{r}
options(warn=-1)
accuracy_scores_2 <- cbind(testing_set_index=rep(0, nrow(combos_list_3)),
                              build_score_list(viruses[viruses$Index==1], combos_list_3, pipeline=2))
for (i in 2:10) {
  accuracy_scores_2 <- rbind(accuracy_scores_2,
                           cbind(testing_set_index=rep(i, nrow(combos_list_3)),
                              build_score_list(viruses[viruses$Index==i], combos_list_3, pipeline=2)))
}
```

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
ggplot(accuracy_scores_2, aes(x=toolcombo, y=F1)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("F1 Score")
ggplot(accuracy_scores_2, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores_2, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("Recall")
```

## Calculate the performance of each pipeline
rule set from DW paper

```{r}
combos_list_3 <- read_csv("combinations_list_3.csv")
```

```{r}
options(warn=-1)
accuracy_scores_3 <- data.frame(testing_set_index=rep(0, nrow(combos_list_3)*10),
                      precision=rep(0, nrow(combos_list_3)*10),
                       recall=rep(0, nrow(combos_list_3)*10),
                       F1=rep(0, nrow(combos_list_3)*10))
accuracy_scores_3 <- cbind(testing_set_index=rep(1, nrow(combos_list_3)),
                              build_score_list(viruses[viruses$Index==1], combos_list_3, pipeline=3))
for (i in 2:10) {
  accuracy_scores_3 <- rbind(accuracy_scores_3,
                           cbind(testing_set_index=rep(i, nrow(combos_list_3)),
                              build_score_list(viruses[viruses$Index==i], combos_list_3, pipeline=3)))
}
```

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
p2 <- ggplot(accuracy_scores_3, aes(x=toolcombo, y=F1)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("F1 Score")
p2
ggplot(accuracy_scores_3, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores_3, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, VB, VS, VS2)") +
  ylab("Recall")
```

### 2022-10-05 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Updates to rule tuning script visualizations.
Added some to dos to the rule_tuning script.
Added lake michigan and TARA identifying viral contigs directories

```{r setup-library}
library(ggplot2)
library(plyr)
library(reshape2)
library(viridis)
library(tidyr)
library(dplyr)
library(readr)
library(data.table)
```

@@

  auc <- round(auc(truepositive, keep_score),4)

@@

  performance <- c(precision, recall, F1, MCC, auc, fungal_FP, bacterial_FP, viral_FN)
  names(performance) <- c("precision", "recall", "F1", "MCC", "AUC", "fungal_FP",
                          "bacterial_FP", "viral_FN")

@@

```{r}
rocobj <- roc(viruses$truepositive, viruses$keep_score)
rocobj_all <- roc(viruses$truepositive, viruses$keep_score_all)
auc <- round(auc(viruses$truepositive, viruses$keep_score),4)
auc_all <- round(auc(viruses$truepositive, viruses$keep_score_all),4)
#create ROC plot
ggroc(rocobj, colour = 'steelblue', size = 2) +
  ggtitle(paste0('ROC Curve ', '(AUC = ', auc, ')')) +
  coord_equal()
ggroc(rocobj_all, colour = 'green', size = 2) +
  ggtitle(paste0('ROC Curve ', '(AUC = ', auc_all, ')'))
```
Sensitivity: The probability that the model predicts a positive outcome for an observation when indeed the outcome is positive.
Specificity: The probability that the model predicts a negative outcome for an observation when indeed the outcome is negative.

>>>>

```{r setup-library}
library(ggplot2)
library(plyr)
library(reshape2)
library(viridis)
library(tidyr)
library(dplyr)
library(readr)
library(data.table)
library(pROC)
library(here)
```

@@

  AUC <- round(auc(truepositive, keep_score),4)

@@

  performance <- c(precision, recall, F1, MCC, AUC, fungal_FP, bacterial_FP, viral_FN)
  names(performance) <- c("precision", "recall", "F1", "MCC", "AUC", "fungal_FP",
                          "bacterial_FP", "viral_FN")

@@

```{r}
rocobj <- roc(viruses$truepositive, viruses$keep_score)
rocobj_all <- roc(viruses$truepositive, viruses$keep_score_all)
AUC <- round(auc(viruses$truepositive, viruses$keep_score),4)
auc_all <- round(auc(viruses$truepositive, viruses$keep_score_all),4)
#create ROC plot
ggroc(rocobj, colour = 'steelblue', size = 2) +
  ggtitle(paste0('ROC Curve ', '(AUC = ', AUC, ')')) +
  coord_equal()
ggroc(rocobj_all, colour = 'green', size = 2) +
  ggtitle(paste0('ROC Curve ', '(AUC = ', auc_all, ')'))
```
Sensitivity: The probability that the model predicts a positive outcome for an observation when indeed the outcome is positive.
Specificity: The probability that the model predicts a negative outcome for an observation when indeed the outcome is negative.

## Pull out Fungi

```{r}
fungi_1 <- viruses[(viruses$seqtype == "fungi") & (viruses$Kaiju_Viral == "Viruses")]
vb_1 <- read_tsv("/Users/riddellj/Documents/Research/VSTE/Troubleshoot_Fungi/VIBRANT_annotations_metagenomic_testing_set_1.tsv")
vb_1 <- separate(vb_1, col = "scaffold", into = c("seqtype", "contig"), sep="--")
vb_1$contig <- sub("\\.", "_", vb_1$contig)
vb_1_vb_c <- inner_join(vb_1, vb_c, on='contig')
vb_1_vb_c_fungi <- vb_1_vb_c %>% filter(seqtype == "fungi")

fungi_1_vb_1_vb_c_fungi <- inner_join(fungi_1,vb_1_vb_c_fungi, on='contig')

#Examples of "false positive" fungi
# https://www.ncbi.nlm.nih.gov/nuccore/599124765
